\sysfull

### 2018-08-06 paper/asplos19/hwswsetup.tex
Methodology revised

We prototype \sys and use its API to implement a set of benchmark
applications representative of the embedded domain. We build the applications
and deploy the binaries onto a real energy-harvesting device. In this section
we describe the setup for the experiments presented in
Section~\ref{sec:evaluation} and characterize the benchmark applications.

@@

We evaluated \sys using six benchmarks that are oftenly used in embedded systems (summarized in
Table~\ref{table:benchmark_table}). All applications were compiled using MSP430 GCC~\cite{ti-gcc} version 6.4.0 toolchain with \texttt{-O1} as optimization flag. The source code for all benchmarks will be released at \cite{coala_website}.

@@

We compare \sys against Alpaca~\cite{alpaca}, the state-of-the-art task-based system for
intermittent computing. For a fair comparison the task decomposition of the benchmarks are ensured to be the
same for both systems.
%
\note{try to reduce what follows}
%
Since Alpaca's compiler pass is implemented only for LLVM, we could not use
that implementation to instrument the benchmarks and compile them with GCC.
Instead, we \emph{manually} performed the instrumentation done by the compiler
pass. The instrumentation consists of identifying write-after-read dependencies 
and adding code and memory allocations to make a private copy of the affected variables. 
For array variables, instrumentation also includes adding code for 
dynamically tracking the array access. Manual instrumentation of Alpaca code is not a general approach, 
but only served as a practical alternative to porting the compiler pass from LLVM to GCC.
%
Our experiments show that manually-instrumented Alpaca code compiled with GCC
is about 30\%-40\% faster than Alpaca code instrumented automatically by the
Alpaca LLVM compiler pass and compiled with LLVM. This performance difference
is due to the early experimental state of the MSP430 backend for
LLVM~\cite{baghsorkhi_cgo_2018}.
%
By compiling both systems with the same compiler (GCC), we ensure that our
comparison in Section~\ref{sec:evaluation} is fair.

>>>>

We prototype \sys and use its API to implement a set of benchmark applications representative of the embedded domain. We build the applications and deploy the binaries onto a real energy-harvesting device.

%In this section we describe the setup for the experiments presented in Section~\ref{sec:evaluation} and characterize the benchmark applications.

@@

We evaluated \sys using six benchmarks that are often used in embedded systems (summarized in Table~\ref{table:benchmark_table}). All applications were compiled using MSP430 GCC~\cite{ti-gcc} version 6.4.0 toolchain with \texttt{-O1} as optimization flag. The source code for all benchmarks will be released at \cite{coala_website}.

@@

We compare \sys against Alpaca~\cite{alpaca}, the state-of-the-art task-based system for intermittent computing. For a fair comparison the task decomposition of the benchmarks are ensured to be the same for both systems.

Since Alpaca's compiler pass is implemented only for LLVM, we could not use that implementation to instrument the benchmarks and compile them with GCC. Instead, we \emph{manually} performed the instrumentation done by the compiler pass. The instrumentation consists of identifying WAR dependencies  and adding code and memory allocations to make a private copy of the affected variables.  For array variables, instrumentation also includes adding code for dynamically tracking the array access.

%Manual instrumentation of Alpaca code is not a general approach, but only served as a practical alternative to porting the compiler pass from LLVM to GCC.
%
%Our experiments show that manually-instrumented Alpaca code compiled with GCC is about 30\%-40\% faster than Alpaca code instrumented automatically by the Alpaca LLVM compiler pass and compiled with LLVM. This performance difference is due to the early experimental state of the MSP430 backend for LLVM~\cite{baghsorkhi_cgo_2018}.
%
By compiling both systems with the same compiler (GCC), we ensure that our comparison in Section~\ref{sec:evaluation} is fair.
